
% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=757575]
\definecolor[rulecolor][h=757575]
%\definecolor[sectioncolor][h=397249]
%\definecolor[rulecolor][h=9cb770]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[10pt, helvetica]

\setupwhitespace[small]

\setupblackrules[width=29.5mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace~}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setupcaptions[table][location=none]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[normal]},
   indentnext=no,
  ]


\starttext

\section[angus-j.-ferraro]{Angus J. Ferraro}

\placetable[none]{}
\starttable[|l|l|]
\HL
\NC College of Engineering,
\NC Email: a.j.ferraro@exeter.ac.uk
\NC\AR
\NC Mathematics and Physical Sciences
\NC Telephone: +44 (0) 1392 725358
\NC\AR
\NC University of Exeter
\NC Web:
\useURL[url1][http://emps.exeter.ac.uk/mathematics/staff/ajf223][][emps.exeter.ac.uk/mathematics/staff/ajf223]\from[url1]
\NC\AR
\NC North Park Road,
\NC Twitter:
\useURL[url2][http://twitter.com/angusferraro][][angusferraro]\from[url2]
\NC\AR
\NC Exeter, EX4 4QF, UK
\NC 
\NC\AR
\HL
\stoptable

\placetable[none]{}
\starttable[|lp(0.88\textwidth)|]
\HL
\NC I am a physical climate scientist with interests in the terrestrial
hydrological cycle and atmospheric radiative transfer. I use climate
model simulations in conjunction with remote sensing observations to
enhance fundamental physical understanding of the climate system. I am
also interested in the emerging technology of climate geoengineering and
how this interacts with conventional climate policy.
\NC\AR
\HL
\stoptable

\subsection[education]{Education}

\startdescription{2010-2014}
  {\bf PhD, Atmosphere, Oceans and Climate}, University of Reading,
  Reading, UK

  \useURL[url3][http://dx.doi.org/10.6084/m9.figshare.1014284][][Atmospheric
  responses to geoengineering in the stratosphere]\from[url3]

  Investigating the impacts of an enhanced stratospheric sulphate layer
  on stratospheric dynamics and communication of these effects to the
  troposphere. Supervisors: Dr.~Andrew Charlton-Perez and Prof.~Eleanor
  Highwood.
\stopdescription

\startdescription{2007-2010}
  {\bf BSc, Meteorology} (First Class Honours), University of Reading,
  Reading, UK

  Dissertation: Factors influencing the climate sensitivity parameter in
  a zero-dimensional climate model. Supervisor: Prof.~Keith Shine.
\stopdescription

\subsection[employment]{Employment}

\startdescription{2014 - present}
  {\bf Research Fellow}, University of Exeter, Exeter, UK

  {\em Process-Based Emergent Physical and Biogeochemical Feedbacks}

  Constraints on the lapse rate, water vapour and cloud climate
  feedbacks. Collaborators: Prof.~Mat Collins and Dr.~Hugo Lambert.
\stopdescription

\startdescription{2009}
  {\bf Research assistant}, Met Office, Exeter, UK

  {\em Impacts of Arctic sea ice retreat on ocean-atmosphere coupling}.
  Supervisor: Dr.~Peili Wu.
\stopdescription

\subsection[competitive-funding]{Competitive Funding}

\startdescription{2015}
  {\bf EPSRC Vacation Bursary} to fund summer student (£2000)
\stopdescription

\startdescription{2011}
  {\bf Travel grant} to attend 2nd Transdisciplinary Summer School on
  Climate Engineering, Banff (USD 1000)
\stopdescription

\subsection[awards-and-recognition]{Awards and Recognition}

\startdescription{Awards}
  \useURL[url4][http://dx.doi.org/10.6084/m9.figshare.1428537][][Runner-up]\from[url4],
  College of Engineering, Mathematics and Physical Sciences Early-Career
  Researcher poster competition, 2015.

  Overall Undergraduate Prize for academic excellence, University of
  Reading, 2010
\stopdescription

\startdescription{Media}
  \useURL[url5][http://www.theengineer.co.uk/in-depth/your-questions-answered-geoengineering/1018992.article][][Your
  questions answered: geoengineering]\from[url5] (question-and-answer
  including me, Stephen Salter, Richard Darton and Andrew
  Charlton-Perez), The Engineer, 2014.

  \useURL[url6][http://environmentalresearchweb.org/cws/article/news/55832][][Sulphate
  geoengineering would harm tropical climate]\from[url6], Environmental
  Research Web, 2014.

  \useURL[url7][http://www.walker-institute.ac.uk/publications/brochures/WalkerHighlights2012WEB.pdf][][Reflecting
  the Sun's energy to cool the planet]\from[url7], Walker Institute
  Research Highlights, 2012.

  \useURL[url8][http://dx.doi.org/10.1038/nclimate1407][][Aerosol
  choices matter]\from[url8], {\em Nature Climate Change}, {\bf 2}, 75,
  2012, doi:10.1038/nclimate1407.
\stopdescription

\subsection[teaching-experience]{Teaching Experience}

\startdescription{2015}
  {\bf Lecturer at University of Exeter Summer School on Global Climate
  Change.} {\em Bringing it home - regional climate variability and
  change.} July 2015

  {\bf Supervision of summer student}. {\em Direct and indirect drivers
  of precipitation change in a geoengineered world.} June-July 2015.
\stopdescription

\startdescription{2014-2015}
  {\bf Co-supervision of MMath student} with Hugo Lambert (University of
  Exeter) and contributions from Manoj Joshi (University of East Anglia)

  {\em Geoengineering and the tropical overturning circulation}
\stopdescription

\startdescription{2011-2013}
  {\bf Demonstrator/tutor} for undergraduates at Department of
  Meteorology, University of Reading

  {\em Introduction to Atmospheric Science}

  {\em Fluid Dynamics of Atmosphere and Oceans}
\stopdescription

\subsection[invited-presentations]{Invited Presentations}

\startdescription{2015}
  {\em Bringing it home: regional climate change and variability}.
  Lecture at University of Exeter International Summer School on Global
  Climate Change: Environment, Technology and Society.
\stopdescription

\startdescription{2013}
  \useURL[url9][http://dx.doi.org/10.6084/m9.figshare.1391985][][{\em Stratospheric
  dynamics in a geoengineered world}]\from[url9]. Seminar at Department
  of Chemistry, University of Cambridge.

  {\em Geoengineering aerosols and how they might affect climate and
  circulation}. IOP Environmental Physics Members' Day, London.
\stopdescription

\startdescription{2012}
  {\em Atmospheric responses to geoengineering in the stratosphere}.
  RMetS South-East local centre meeting, Reading.
\stopdescription

\subsection[selected-presentations]{Selected Presentations}

\startdescription{2016}
  {\em Classification of land-sea shifts in tropical precipitation using
  temperature and moisture change}, (poster), Workshop on Atmospheric
  Circulation and Regional Climate Change, University of Reading, UK.
\stopdescription

\startdescription{2015}
  {\em Physical mechanisms of tropical climate feedbacks revealed by
  temperature and moisture trends},
  \useURL[url10][[http://dx.doi.org/10.6084/m9.figshare.1428537][][(poster)]\from[url10]
  AGU Fall Meeting, San Francisco, USA.

  {\em Physical mechanisms of tropical climate feedbacks revealed by
  temperature and moisture trends},
  \useURL[url11][[http://dx.doi.org/10.6084/m9.figshare.1428537][][(poster)]\from[url11]
  CFMIP conference, Asilomar, USA.

  {\em Physical mechanisms of tropical climate feedbacks revealed by
  temperature and moisture trends},
  \useURL[url12][http://dx.doi.org/10.6084/m9.figshare.1335975][][(poster)]\from[url12]
  EGU General Assembly, Vienna, Austria.
\stopdescription

\startdescription{2013}
  {\em Effects of different geoengineering aerosol choices on
  stratospheric dynamics}, (poster) 3rd NCAS Chemistry-Climate
  Interaction Meeting, Cambridge, UK.

  {\em Impact of aerosol & dimmed-sun geoengineering on stratospheric
  dynamics}, 3rd GeoMIP workshop, Potsdam, Germany.

  {\em Atmospheric responses to stratospheric aerosol geoengineering},
  EGU General Assembly, Vienna, Austria.
\stopdescription

\startdescription{2012}
  {\em Stratospheric heating by geoengineering aerosols}, 2nd GeoMIP
  workshop, Exeter, UK.
\stopdescription

\subsection[professional-activities]{Professional Activities}

\startitemize[packed]
\item
  Peer reviewer for {\em Environmental Research Letters}, {\em Journal
  of Geophysical Research} and others. Full review record available via
  \useURL[url13][https://publons.com/author/589854/angus-ferraro\#profile][][Publons]\from[url13].
\item
  Grant application reviewer for US National Science Foundation.
\stopitemize

\startdescription{2015-present}
  Member of American Geophysical Union
\stopdescription

\startdescription{2013-present}
  Member of European Geoscience Union
\stopdescription

\startdescription{2010-present}
  Member of Royal Meteorological Society
\stopdescription

\subsection[outreach]{Outreach}

Personal
\useURL[url14][http://angusferraro.wordpress.com][][blog]\from[url14]
summarising recent advances in climate science; contributions to the WCD
blog (Department of Meteorology, University of Reading), the GeoBlog
(Oxford Geoengineering Programme, University of Oxford) and the GeoLog
(European Geosciences Union).

\startdescription{2015}
  Contributor on geoengineering for Simon Clark's YouTube series,
  \quote{Crash Course in Atmospheric Physics}.

  \quote{Britain Needs Scientists} schools event, University of Exeter.
\stopdescription

\startdescription{2013}
  Runner-up in
  \useURL[url15][http://earthj13.imascientist.org.uk/profile/angusferraro/][][I'm
  a Scientist, Get Me Out of Here]\from[url15].

  Finalist in University of Reading \quote{3-minute thesis} competition.
\stopdescription

\startdescription{2011-2013}
  Volunteer classroom science assistant at Highdown School, Reading.
\stopdescription

\subsection[responsibilities]{Responsibilities}

\startdescription{2014-present}
  Convenor of Physical Climate Research Group at Exeter Climate Systems,
  University of Exeter
\stopdescription

\startdescription{2014}
  Organiser of Exeter Climate Systems collaborative research day.
\stopdescription

\startdescription{2011-2013}
  Convenor of Stratosphere & Climte Research Group and Strathour seminar
  series at Department of Meteorology, University of Reading
\stopdescription

\startdescription{2011}
  Member of \quote{Visiting Scientist} committee at Department of
  Meteorology, University of Reading (visitor: Kevin Trenberth)
\stopdescription

\subsection[publications]{Publications}

Ferraro, A. J. and H. G. Griffiths, 2016: Quantifying the
temperature-independent effect of stratospheric aerosol geoengineering
on global-mean precipitation in a multi- model ensemble.
{\em Environmental Research Letters}, {\bf 11}, 034012,
doi:\useURL[url16][http://10.1088/1748-9326/11/3/034012][][10.1088/1748-9326/11/3/034012]\from[url16].

Ferraro, A. J., F. H. Lambert, M. Collins, and G. Miles, 2015: Physical
mechanisms of tropical climate feedbacks revealed by temperature and
moisture trends. {\em Journal of Climate}, {\bf 28}, 8968-8987,
doi:\useURL[url17][http://10.1175/JCLI-D-15-0253.1][][10.1175/JCLI-D-15-0253.1]\from[url17].

Ferraro, A. J., M. Collins, and F. H. Lambert, 2015: A hiatus in the
stratosphere?. {\em Nature Climate Change}, {\bf 5}, 497-498,
doi:\useURL[url18][http://dx.doi.org/10.1038/nclimate2624][][10.1038/nclimate2624]\from[url18].

\startblockquote
Citations: 1
\stopblockquote

Ferraro, A. J., A. J. Charlton-Perez, and E. J. Highwood, 2015:
Stratospheric dynamics and midlatitude jets under geoengineering with
space mirrors and sulfate and titania aerosols. {\em J. Geophys. Res.
Atmos.}, {\bf 120}, 414-429,
doi:\useURL[url19][http://dx.doi.org/10.1002/2014jd022734][][10.1002/2014jd022734]\from[url19].

Ferraro, A. J., A. J. Charlton-Perez, and E. J. Highwood, 2014: A
Risk-Based Framework for Assessing the Effectiveness of Stratospheric
Aerosol Geoengineering. {\em PLoS ONE}, {\bf 9}, e88849,
doi:\useURL[url20][http://dx.doi.org/10.1371/journal.pone.0088849][][10.1371/journal.pone.0088849]\from[url20].

\startblockquote
Citations: 3
\stopblockquote

\startblockquote
Part of the PLOS \quote{Responding to Climate Change} collection
\stopblockquote

Ferraro, A. J., E. J. Highwood, and A. J. Charlton-Perez, 2014: Weakened
tropical circulation and reduced precipitation in response to
geoengineering. {\em Environ. Res. Lett.}, {\bf 9}, 014001,
doi:\useURL[url21][http://dx.doi.org/10.1088/1748-9326/9/1/014001][][10.1088/1748-9326/9/1/014001]\from[url21].

\startblockquote
Citations: 9
\stopblockquote

\startblockquote
One of 25 highlights of 2014 in {\em Environmental Research Letters}
\stopblockquote

\startblockquote
Extensive media coverage including BBC, Guardian, The Independent,
phys.org, New Zealand Herald, Bangkok Post, Hindustan Times.
\stopblockquote

Ferraro, A. J., E. J. Highwood, and A. J. Charlton-Perez, 2011:
Stratospheric heating by potential geoengineering aerosols.
{\em Geophysical Research Letters}, {\bf 38},
doi:\useURL[url22][http://dx.doi.org/10.1029/2011gl049761][][10.1029/2011gl049761]\from[url22].

\startblockquote
Citations: 13
\stopblockquote

\startblockquote
Research Highlight in {\em Nature Climate Change}
\stopblockquote

\stoptext
